Self-reported LLM usage and results on a data science project: Evidence from a Canadian undergraduate data science course

### 2024-08-12 paper/paper.qmd
Reorder rows in Table 2a from Very familiar to Not familiar

all_data |>
  rename(ai_familiarity = how_familiar_are_you_with_using_generative_ai_tools_such_as_open_a_is_chat_gpt_or_equivalents) |>
  mutate(
    ai_familiarity = case_when(
      ai_familiarity == "Limited to some liberal arts, such as history courses" ~ "Somewhat familiar",
      TRUE ~ ai_familiarity
    )
  ) |>
  count(ai_familiarity) |>
  kable(col.names = c("Extent of AI familiarity", "Students"))

>>>>

all_data |>
  rename(ai_familiarity = how_familiar_are_you_with_using_generative_ai_tools_such_as_open_a_is_chat_gpt_or_equivalents) |>
  mutate(
    ai_familiarity = case_when(
      ai_familiarity == "Limited to some liberal arts, such as history courses" ~ "Somewhat familiar",
      TRUE ~ ai_familiarity
    )
  ) |>
  mutate(
     ai_familiarity = factor(ai_familiarity, levels=c("Very familiar", "Somewhat familiar", "Not familiar"))
     ) |>
  count(ai_familiarity) |>
  kable(col.names = c("Extent of AI familiarity", "Students"))
